%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\begin{flushright}{\slshape
    Don’t wish it was easier wish you were better. \\
    Don’t wish for less problems wish for more skills. \\
    Don’t wish for less challenge wish for more wisdom.} \\ \medskip
    --- \defcitealias{knuth:1974}{Jim Rohn}\citetalias{knuth:1974}
\end{flushright}



\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
Put your acknowledgments here.

Many thanks to everybody who already sent me a postcard!

Regarding the typography and other help, many thanks go to Marco
Kuhlmann, Philipp Lehman, Lothar Schlesier, Jim Young, Lorenzo
Pantieri and Enrico Gregorio, J\"org Sommer,
Joachim K\"ostler, Daniel Gottschlag, Denis Aydin, Paride
Legovini, Steffen Prochnow, Nicolas Repp, Hinrich Harms,
Roland Winkler, Jörg Weber, Henri Menke, Claus Lahiri,
Clemens Niederberger, Stefano Bragaglia, Jörn Hees,
Scott Lowe, Dave Howcroft, Jos\'e M. Alcaide, David Carlisle,
Ulrike Fischer, Hugues de Lassus, Csaba Hajdu, Dave Howcroft,
Anonymous, Konrad Höffner, 
and the whole \LaTeX-community for support, ideas and
some great software.

\bigskip

\noindent\emph{Regarding \mLyX}: The \mLyX\ port was intially done by
\emph{Nicholas Mariette} in March 2009 and continued by
\emph{Ivo Pletikosi\'c} in 2011. Thank you very much for your
work and for the contributions to the original style.


\endgroup
